The sound of teaching music: Expert pianists' performance modulations for novices

### 2022-09-01 paper/manuscript.Rmd
add captions for figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r art-teaching-1, include = FALSE}
kot_art_plot$teachingexp <- factor(kot_art_plot$teachingexp, levels = c("Yes", "No"))

@@

```{r dyn-teaching-1, include = FALSE}
vel_dyn_plot$teachingexp <- factor(vel_dyn_plot$teachingexp, levels = c("Yes", "No"))

@@

```{r dyn-diff-teaching-1, include = FALSE}
vel_diff_dyn_plot$teachingexp <- factor(vel_diff_dyn_plot$teachingexp, levels = c("Yes", "No"))

@@

```{r plot-ioi-teaching-1, out.width = "100%", fig.cap = "\\label{fig:ioi-teaching-1}BAA"}
img_ioi_teaching_1 <- image_append(c(img_ioi_art_teaching_1, img_ioi_dyn_teaching_1))
image_write(img_ioi_teaching_1, path = here("paper/figure", "Fig13.tiff"), format = "tiff")
img_ioi_teaching_1
```

```{r plot-art-teaching-1, out.width = "100%", fig.cap = "\\label{fig:art-teaching-1}BAA"}
img_art_teaching_1 <- image_append(c(img_art_leg_teaching_1, img_art_sta_teaching_1))
image_write(img_art_teaching_1, path = here("paper/figure", "Fig14.tiff"), format = "tiff")
img_art_teaching_1
```

```{r plot-dyn-teaching-1, out.width = "100%", fig.cap = "\\label{fig:dyn-teaching-1}BAA"}
img_dyn_teaching_1 <- image_append(c(img_vel_for_teaching_1, img_vel_pia_teaching_1))
image_write(img_dyn_teaching_1, path = here("paper/figure", "Fig15.tiff"), format = "tiff")
img_dyn_teaching_1
```

```{r plot-dyn-diff-teaching-1, out.width = "100%", fig.cap = "\\label{fig:dyn-diff-teaching-1}BAA"}
img_dyn_diff_teaching_1 <- image_append(c(img_vel_diff_for_teaching_1, img_vel_diff_pia_teaching_1))
image_write(img_dyn_diff_teaching_1, path = here("paper/figure", "Fig16.tiff"), format = "tiff")
img_dyn_diff_teaching_1
```

@@

apa_table(
  ioi_all
  , caption = "Caption"
  , note = "Note"
  , escape = TRUE
)
```

@@

apa_table(
  kot_art_all
  , caption = "Caption"
  , note = "Note"
  , escape = TRUE
)
```

@@

apa_table(
  vel_dyn_all
  , caption = "Caption"
  , note = "Note"
  , escape = TRUE
)
```

@@

apa_table(
  vel_diff_dyn_all
  , caption = "Caption"
  , note = "Note"
  , escape = TRUE
)
```

@@

```{r plot-ioi-teaching-2, out.width = "100%", fig.cap = "\\label{fig:ioi-teaching-2}BAA"}
img_ioi_teaching_2 <- image_append(c(img_ioi_art_teaching_2, img_ioi_dyn_teaching_2))
image_write(img_ioi_teaching_2, path = here("paper/figure", "Fig17.tiff"), format = "tiff")
img_ioi_teaching_2
```

```{r plot-art-teaching-2, out.width = "100%", fig.cap = "\\label{fig:art-teaching-2}BAA"}
img_art_teaching_2 <- image_append(c(img_art_leg_teaching_2, img_art_sta_teaching_2))
image_write(img_art_teaching_2, path = here("paper/figure", "Fig18.tiff"), format = "tiff")
img_art_teaching_2
```

```{r plot-dyn-teaching-2, out.width = "100%", fig.cap = "\\label{fig:dyn-teaching-2}BAA"}
img_dyn_teaching_2 <- image_append(c(img_vel_for_teaching_2, img_vel_pia_teaching_2))
image_write(img_dyn_teaching_2, path = here("paper/figure", "Fig19.tiff"), format = "tiff")
img_dyn_teaching_2
```

```{r plot-dyn-diff-teaching-2, out.width = "100%", fig.cap = "\\label{fig:dyn-diff-teaching-2}BAA"}
img_dyn_diff_teaching_2 <- image_append(c(img_vel_diff_for_teaching_2, img_vel_diff_pia_teaching_2))
image_write(img_dyn_diff_teaching_2, path = here("paper/figure", "Fig20.tiff"), format = "tiff")
img_dyn_diff_teaching_2
```

@@

apa_table(
  ioi_all
  , caption = "Caption"
  , note = "Note"
  , escape = TRUE
  , digits = 3
)
```

@@

apa_table(
  kor_art_all
  , caption = "Caption"
  , note = "Note"
  , escape = TRUE
  , digits = 3
)
```

@@

apa_table(
  vel_dyn_all
  , caption = "Caption"
  , note = "Note"
  , escape = TRUE
)
```

@@

apa_table(
  vel_diff_dyn_all
  , caption = "Caption"
  , note = "Note"
  , escape = TRUE
)
```

>>>>

```{r art-teaching-1, include = FALSE}
# articulation
kot_art_plot$teachingexp <- factor(kot_art_plot$teachingexp, levels = c("Yes", "No"))

@@

```{r dyn-teaching-1, include = FALSE}
# dynamics
vel_dyn_plot$teachingexp <- factor(vel_dyn_plot$teachingexp, levels = c("Yes", "No"))

@@

```{r dyn-diff-teaching-1, include = FALSE}
# dynamics difference
vel_diff_dyn_plot$teachingexp <- factor(vel_diff_dyn_plot$teachingexp, levels = c("Yes", "No"))

@@

```{r plot-ioi-teaching-1, out.width = "100%", fig.cap = "\\label{fig:ioi-teaching-1}Experiment 1: Comparison between those with and without piano teaching experience in terms of IOIs (ms) when playing the piece with either articulation (left) or dynamics (right). A dashed line represents the tempo given by a metronome. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
img_ioi_teaching_1 <- image_append(c(img_ioi_art_teaching_1, img_ioi_dyn_teaching_1))
image_write(img_ioi_teaching_1, path = here("paper/figure", "Fig13.tiff"), format = "tiff")
img_ioi_teaching_1
```

```{r plot-art-teaching-1, out.width = "100%", fig.cap = "\\label{fig:art-teaching-1}Experiment 1: Comparison between those with and without piano teaching experience in terms of KOT (ms) when playing the piece with articulation. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
img_art_teaching_1 <- image_append(c(img_art_leg_teaching_1, img_art_sta_teaching_1))
image_write(img_art_teaching_1, path = here("paper/figure", "Fig14.tiff"), format = "tiff")
img_art_teaching_1
```

```{r plot-dyn-teaching-1, out.width = "100%", fig.cap = "\\label{fig:dyn-teaching-1}Experiment 1: Comparison between those with and without piano teaching experience in terms of KV (0-127) when playing the piece with dynamics. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
img_dyn_teaching_1 <- image_append(c(img_vel_for_teaching_1, img_vel_pia_teaching_1))
image_write(img_dyn_teaching_1, path = here("paper/figure", "Fig15.tiff"), format = "tiff")
img_dyn_teaching_1
```

```{r plot-dyn-diff-teaching-1, out.width = "100%", fig.cap = "\\label{fig:dyn-diff-teaching-1}Experiment 1: Comparison between those with and without piano teaching experience in terms of KV Difference at transition points when playing the piece with dynamics. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
img_dyn_diff_teaching_1 <- image_append(c(img_vel_diff_for_teaching_1, img_vel_diff_pia_teaching_1))
image_write(img_dyn_diff_teaching_1, path = here("paper/figure", "Fig16.tiff"), format = "tiff")
img_dyn_diff_teaching_1
```

@@

apa_table(
  ioi_all
  , caption = "Experiment 1:"
  , note = "Note"
  , escape = TRUE
)
```

@@

apa_table(
  kot_art_all
  , caption = "Experiment 1:"
  , note = "Note"
  , escape = TRUE
)
```

@@

apa_table(
  vel_dyn_all
  , caption = "Experiment 1:"
  , note = "Note"
  , escape = TRUE
)
```

@@

apa_table(
  vel_diff_dyn_all
  , caption = "Experiment 1:"
  , note = "Note"
  , escape = TRUE
)
```

@@

```{r plot-ioi-teaching-2, out.width = "100%", fig.cap = "\\label{fig:ioi-teaching-2}Experiment 2: Comparison between those with and without piano teaching experience in terms of IOIs (ms) when playing the piece with either articulation (left) or dynamics (right). A dashed line represents the tempo given by a metronome. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
img_ioi_teaching_2 <- image_append(c(img_ioi_art_teaching_2, img_ioi_dyn_teaching_2))
image_write(img_ioi_teaching_2, path = here("paper/figure", "Fig17.tiff"), format = "tiff")
img_ioi_teaching_2
```

```{r plot-art-teaching-2, out.width = "100%", fig.cap = "\\label{fig:art-teaching-2}Experiment 2:  Comparison between those with and without piano teaching experience in terms of KOT (ms) when playing the piece with articulation. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
img_art_teaching_2 <- image_append(c(img_art_leg_teaching_2, img_art_sta_teaching_2))
image_write(img_art_teaching_2, path = here("paper/figure", "Fig18.tiff"), format = "tiff")
img_art_teaching_2
```

```{r plot-dyn-teaching-2, out.width = "100%", fig.cap = "\\label{fig:dyn-teaching-2}Experiment 2: Comparison between those with and without piano teaching experience in terms of KV (0-127) when playing the piece with dynamics. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
img_dyn_teaching_2 <- image_append(c(img_vel_for_teaching_2, img_vel_pia_teaching_2))
image_write(img_dyn_teaching_2, path = here("paper/figure", "Fig19.tiff"), format = "tiff")
img_dyn_teaching_2
```

```{r plot-dyn-diff-teaching-2, out.width = "100%", fig.cap = "\\label{fig:dyn-diff-teaching-2}Experiment 2: Comparison between those with and without piano teaching experience in terms of KV Difference at transition points when playing the piece with dynamics. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box."}
img_dyn_diff_teaching_2 <- image_append(c(img_vel_diff_for_teaching_2, img_vel_diff_pia_teaching_2))
image_write(img_dyn_diff_teaching_2, path = here("paper/figure", "Fig20.tiff"), format = "tiff")
img_dyn_diff_teaching_2
```

@@

apa_table(
  ioi_all
  , caption = "Experiment 2:"
  , note = "Note"
  , escape = TRUE
  , digits = 3
)
```

@@

apa_table(
  kor_art_all
  , caption = "Experiment 2:"
  , note = "Note"
  , escape = TRUE
  , digits = 3
)
```

@@

apa_table(
  vel_dyn_all
  , caption = "Experiment 2:"
  , note = "Note"
  , escape = TRUE
)
```

@@

apa_table(
  vel_diff_dyn_all
  , caption = "Experiment 2:"
  , note = "Note"
  , escape = TRUE
)
```

### 2022-09-01 paper/manuscript.tex
add captions for figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-ioi-teaching-1-1} \caption{\label{fig:ioi-teaching-1}BAA}\label{fig:plot-ioi-teaching-1}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-art-teaching-1-1} \caption{\label{fig:art-teaching-1}BAA}\label{fig:plot-art-teaching-1}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-teaching-1-1} \caption{\label{fig:dyn-teaching-1}BAA}\label{fig:plot-dyn-teaching-1}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-diff-teaching-1-1} \caption{\label{fig:dyn-diff-teaching-1}BAA}\label{fig:plot-dyn-diff-teaching-1}
\end{figure}

@@

\caption{\label{tab:ioi-teaching-desc-1}Caption}

@@

\caption{\label{tab:art-teaching-desc-1}Caption}

@@

\caption{\label{tab:dyn-teaching-desc-1}Caption}

@@

\caption{\label{tab:dyn-diff-teaching-desc-1}Caption}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-ioi-teaching-2-1} \caption{\label{fig:ioi-teaching-2}BAA}\label{fig:plot-ioi-teaching-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-art-teaching-2-1} \caption{\label{fig:art-teaching-2}BAA}\label{fig:plot-art-teaching-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-teaching-2-1} \caption{\label{fig:dyn-teaching-2}BAA}\label{fig:plot-dyn-teaching-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-diff-teaching-2-1} \caption{\label{fig:dyn-diff-teaching-2}BAA}\label{fig:plot-dyn-diff-teaching-2}
\end{figure}

@@

\caption{\label{tab:ioi-teaching-desc-2}Caption}

@@

\caption{\label{tab:art-teaching-desc-2}Caption}

@@

\caption{\label{tab:dyn-teaching-desc-2}Caption}

@@

\caption{\label{tab:dyn-diff-teaching-desc-2}Caption}

>>>>

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-ioi-teaching-1-1} \caption{\label{fig:ioi-teaching-1}Experiment 1: Comparison between those with and without piano teaching experience in terms of IOIs (ms) when playing the piece with either articulation (left) or dynamics (right). A dashed line represents the tempo given by a metronome. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-ioi-teaching-1}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-art-teaching-1-1} \caption{\label{fig:art-teaching-1}Experiment 1: Comparison between those with and without piano teaching experience in terms of KOT (ms) when playing the piece with articulation. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-art-teaching-1}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-teaching-1-1} \caption{\label{fig:dyn-teaching-1}Experiment 1: Comparison between those with and without piano teaching experience in terms of KV (0-127) when playing the piece with dynamics. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-dyn-teaching-1}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-diff-teaching-1-1} \caption{\label{fig:dyn-diff-teaching-1}Experiment 1: Comparison between those with and without piano teaching experience in terms of KV Difference at transition points when playing the piece with dynamics. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-dyn-diff-teaching-1}
\end{figure}

@@

\caption{\label{tab:ioi-teaching-desc-1}Experiment 1:}

@@

\caption{\label{tab:art-teaching-desc-1}Experiment 1:}

@@

\caption{\label{tab:dyn-teaching-desc-1}Experiment 1:}

@@

\caption{\label{tab:dyn-diff-teaching-desc-1}Experiment 1:}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-ioi-teaching-2-1} \caption{\label{fig:ioi-teaching-2}Experiment 2: Comparison between those with and without piano teaching experience in terms of IOIs (ms) when playing the piece with either articulation (left) or dynamics (right). A dashed line represents the tempo given by a metronome. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-ioi-teaching-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-art-teaching-2-1} \caption{\label{fig:art-teaching-2}Experiment 2:  Comparison between those with and without piano teaching experience in terms of KOT (ms) when playing the piece with articulation. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-art-teaching-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-teaching-2-1} \caption{\label{fig:dyn-teaching-2}Experiment 2: Comparison between those with and without piano teaching experience in terms of KV (0-127) when playing the piece with dynamics. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-dyn-teaching-2}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/plot-dyn-diff-teaching-2-1} \caption{\label{fig:dyn-diff-teaching-2}Experiment 2: Comparison between those with and without piano teaching experience in terms of KV Difference at transition points when playing the piece with dynamics. Each box indicates the IQR with the median, and whiskers extend to a maximum of 1.5 × IQR beyond the box.}\label{fig:plot-dyn-diff-teaching-2}
\end{figure}

@@

\caption{\label{tab:ioi-teaching-desc-2}Experiment 2:}

@@

\caption{\label{tab:art-teaching-desc-2}Experiment 2:}

@@

\caption{\label{tab:dyn-teaching-desc-2}Experiment 2:}

@@

\caption{\label{tab:dyn-diff-teaching-desc-2}Experiment 2:}
